---
title: "A2-Dataset-2"
format:
  html:
    css: styles.css
---

# Valentine's Day Spending

```{r setup, echo=FALSE}
suppressMessages({
library(tidyverse)
library(mosaic)
library(skimr)
library(ggformula)
library(ggprism)
library(kableExtra)
  library(ggnewscale)
})
```

------------------------------------------------------------------------

<button>[Examining the Data]{.button_top}</button>

------------------------------------------------------------------------

```{r}
gifts_age <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-02-13/gifts_age.csv")
glimpse(gifts_age)
```

```{r}
inspect(gifts_age)
```

------------------------------------------------------------------------

<button>[Data Munging & Creating Data Dictionary]{.button_top}</button>

------------------------------------------------------------------------

```{r}
giftsage_modified <- gifts_age %>%
   mutate(Age = as.factor(Age))
giftsage_modified
```

```{r, echo=FALSE}
data_dictionary <- data.frame(
  Variables = c("Age", "SpendingCelebrating", "Candy", "Flowers", "Jewelry", 
                "GreetingCards", "EveningOut", "Clothing", "GiftCards"),
  Data_types = c("Factor-qual", "Float-quant", "Float-quant", "Float-quant", "Float-quant", 
                 "Float-quant", "Float-quant", "Float-quant", "Float-quant"),
  Desc = c(
    "Age group",
    "Average spending on celebrations",
    "Average spending on candy",
    "Average spending on flowers",
    "Average spending on jewelry",
    "Average spending on greeting cards ",
    "Average spending on evening outings",
    "Average spending on clothing ",
    "Average spending on gift cards"
  )
)


kable(data_dictionary)
```

------------------------------------------------------------------------

<button>[Research Questions]{.button_top}</button>

------------------------------------------------------------------------

Dependent variable- spending

Independent variable - age

-Relation between age and gift categories

-what are the valentine's day spending trends across different age groups

What research activity might have been carried out to obtain the data graphed here?

-   surveys

-   reports on consumer spending

------------------------------------------------------------------------

<button>[plotting graph]{.button_top}</button>

------------------------------------------------------------------------

```{r}
data_long <-gifts_age %>%
  pivot_longer(cols = -Age, names_to = "Category", values_to = "AmountSpent") 

ggplot(data_long, aes(x = Age, y = AmountSpent, color = Category, group = Category)) +
  geom_line(size = 1) +  
  geom_point(size = 2) +  
  labs(title = "Spending by Age Group",
       x = "Age Group",
       y = "Amount Spent",
       color = "Spending Category") +
  theme_minimal() +  
  theme(axis.text.x = element_text(angle = 45, hjust = 1))  

```

### Pre processing: wide to long where all spending categories are combined in one column which becomes our amount spent. 

```{r}
colnames(giftsage_modified)
```

```{r}
colnames(gifts_age)
```

## Observations/surprises

-Did not expect spending on jewellery to be high among the younger age brackets.

\- had a preconceived notion that the 65+ age group would have considerable amounts of spending in the jewellery and flowers categories

-did not expect candy to be plotted so high up either especially for the older age groups.
