---
title: "A1: summaries"
---

## Code Replication for mpg dataset

```{r setup, echo=FALSE}
suppressMessages({
  library(tidyverse)
  library(mosaic)
  library(skimr)
  library(knitr)
  library(kableExtra)
  library(readr)
})

```

-   Reading mpg

    ```{r}
    mpg
    ```

-   Examining the data set using glimpse, inspect and skimr

    ```{r}
    dplyr::glimpse(mpg)
    ```

    ```{r}
    mosaic::inspect(mpg)
    ```

    ```{r}
    skimr::skim(mpg) 
    ```

-   munging

    ```{r}
    mpg_modified <- mpg %>%
      dplyr::mutate(
        cyl = as_factor(cyl),
        fl = as_factor(fl),
        drv = as_factor(drv),
        class = as_factor(class),
        trans = as_factor(trans)
      )
    glimpse(mpg_modified)
    ```

# Math Anxiety

```{r}
math_anxiety <- read_delim("../../data/MathAnxiety.csv", delim = ';')
print(head(math_anxiety))


```

```{r}
math_anxiety
```

# Examining the data

```{r}
dplyr::glimpse(math_anxiety)
```

```{r}
skimr::skim(mpg) 

```

```{r}
mosaic::inspect(math_anxiety)
```

```{r}
skim(math_anxiety) %>%
  kbl(align = "c", caption = "Skim Output for Math anxiety Dataset") %>%
  kable_paper(full_width = F)
```

# Data Dictionary

```{r, echo=FALSE}
data_dictionary <- data.frame(
  Variable_Name = c("Gender", "Grade", "Age", "AMAS", "RCMAS", "Arith"),
  Data_Type = c("Factor", "Character", "Integer", "Numeric", "Numeric", "Numeric"),
  Description = c(
    "Gender",
    "Grade the student is currently in",
    "Age, /120",
    "Type of Exam",
    "Another Exam",
    "Yet another exam"
  )
)
print(data_dictionary)
```

# Data Munging

```{r}
mathanxiety_modified <- math_anxiety %>%
mutate(
    Gender = as.factor(Gender),  
    Age = as.integer(Age / 120)   
  )
glimpse(mathanxiety_modified)
```

## Reading the data again

```{r}
mathanxiety_modified
```

# Questions

-   Is there a difference in anxiety levels between genders across all three exams ?

    ```{r}
    mathanxiety_modified %>%
      group_by(Gender) %>%
      summarise(average_AMAS = mean(AMAS),   
        average_RCMAS = mean(RCMAS),average_Arith = mean(Arith), 
        count = n()                                
      )

    ```

> ### Inferences:
>
> Girls seem to show higher levels of math anxiety across all exams.
>
> Negligible difference in the arith exam between boys and girls.

## similarly for grade...

-   do the anxiety levels vary based on the students' grade level.

    ```{r}
    mathanxiety_modified %>%
      group_by(Grade) %>%
      summarise( average_AMAS = mean(AMAS),   
        average_RCMAS = mean(RCMAS), average_Arith = mean(Arith), 
        count = n()                                
      )


    ```

> ### Inferences:
>
> Anxiety levels seem pretty consistent across both grades.
>
> Primary grade student experience seem to experience higher anxiety levels, also need to take into consideration that their sample size is larger

### Using favstats... overview of anxiety scores across all exams by gender

-   AMA

    ```{r}
    mathanxiety_modified %>%
      mosaic::favstats(AMAS ~ Gender, data = .) 
    ```

<!-- -->

-   Arith

    ```{r}
    mathanxiety_modified %>%
      mosaic::favstats(Arith ~ Gender, data = .) 
    ```

-   RCMAS

    ```{r}
    mathanxiety_modified %>%
      mosaic::favstats(RCMAS ~ Gender, data = .) 
    ```

```{r}
# Check the names of the columns in your dataset
colnames(math_anxiety)

```
