---
title: "A-3 streams"
format:
  html:
    css: styles.css
---

------------------------------------------------------------------------

<button>[Reading the Data]{.button_top}</button>

------------------------------------------------------------------------

```{r setup, echo=FALSE}
suppressMessages({
#| label: setup 
library(tidyverse)
library(ggformula)
library(mosaic)
library(crosstable)
library(broom)
library(ggformula)
library(infer) 
library(patchwork) 
library(ggprism) 
library(supernova) 
library(DescTools)
})
```

# Reading

```{r}
streams <-read.csv("../../data/Art, Design, and Vocation are all diff-different(Sheet1).csv")
print(head(streams))
```

## \## Research Question: **Art, Design, and Vocation are all different?**

# Munging

```{r}
streams_modified <- streams %>%
  mutate(Gender = as.factor(Gender)) %>%
  mutate(Degree = as.factor(Degree))%>%
  mutate(Letter.Grade = as.factor(Letter.Grade))%>%
    mutate(Course = as.factor(Course))

```

# EDA

```{r}
gf_histogram(~Score,
  fill = ~Degree, 
  data = streams_modified, 
  alpha = 0.5,  
  bins = 25  
) %>%
  gf_vline(xintercept = ~ mean(Score, na.rm = TRUE),  
            linetype = "dashed", color = "red") %>%
  gf_labs(
    title = "Histogram of scores across degrees",
    x = "Scores", 
    y = "Count"
  ) %>%
  gf_text(
    label = "Overall Mean", 
    x = mean(streams_modified$Score, na.rm = TRUE),  
    y = 2, 
    color = "red"
  ) %>%
  gf_refine(guides(fill = guide_legend(title = ""))) 

```

```{r}
gf_boxplot(
  data = streams_modified,
  Score ~ Degree,
  fill = ~Degree,
  alpha = 0.5
) %>%
  gf_vline(xintercept = ~ mean(Score, na.rm = TRUE)) %>%
  gf_labs(
    title = "Boxplots of scoress",
    x = "Degree", 
    y = "Scores",
   
  ) %>%
  gf_refine(
    scale_x_discrete(guide = "prism_bracket"),
    guides(fill = guide_legend(title = ""))
  )
```

### - median score for bdes is the highest, lowest is b.voc and bfa lies between the two

-   outliers for b.voc

-   bvoc distribution is skewed left and bdes skewed right with high concentration of scores on higher end

-   bfa distribuion seems to be evenly spread out

# Anova

```{r}
streams_anova <- aov(Score ~ Degree, data = streams_modified)

supernova::pairwise(streams_anova,
  correction = "Bonferroni", # Try "Tukey"
  alpha = 0.05, # 95% CI calculation
  var_equal = TRUE, # We'll see
  plot = TRUE
)
```

### Inferences

-   significant difference between the mean scores of B.FA and B.Des.

-   also a significant difference between the mean scores of B.Voc and B.Des and B.Voc and B.FA.

    <div>

    # B.Des \> B.FA \> B.Voc

    </div>
