---
title: "A-3 pocketmoney"
format:
  html:
    css: styles.css
ORDER: 20
---

------------------------------------------------------------------------

<button>[Reading the Data]{.button_top}</button>

------------------------------------------------------------------------

```{r setup, echo=FALSE}
suppressMessages({
#| label: setup 
library(tidyverse)
library(ggformula)
library(mosaic)
library(crosstable)
library(broom)
library(ggformula)
})
```

```{r}
Pocket_money <-read.csv("../../data/Pocket_money.csv")
print(head(Pocket_money))
```

------------------------------------------------------------------------

## Research Question: Is there a significant difference in the average daily pocket money spent by boys and girls?

------------------------------------------------------------------------

<button>[Examining and Summarising]{.button_top}</button>

------------------------------------------------------------------------

```{r}
inspect(Pocket_money)
```

```{r}
Pocket_money %>% crosstable(Money_spent~Gender) %>% as_flextable()
```

```{r}
mosaic::t_test(Money_spent~Gender, data=Pocket_money)  %>% broom::tidy()
```

------------------------------------------------------------------------

<button>[Data Munging]{.button_top}</button>

------------------------------------------------------------------------

```{r}
library(dplyr)


pm_modified <- Pocket_money %>%
  mutate(Gender = as.factor(Gender))

```

#### Qual variables- Gender

#### Quant variable(s)- Money_spent

------------------------------------------------------------------------

<button>[Plotting Graphs]{.button_top}</button>

------------------------------------------------------------------------

```{r}

pm_modified %>%
  gf_density(
    ~ Money_spent,
    fill = ~ Gender,
    alpha = 0.5,
    title = "Money Spent Densities",
    subtitle = "Male vs Female"
  )
##
pm_modified %>%
  gf_boxplot(
    Money_spent ~ Gender,
    fill = ~ Gender,
    alpha = 0.5,
    title = "Money Spent Box Plots",
    subtitle = "Male vs Female"
  ) %>% gf_refine(scale_y_log10()) 
##
pm_modified %>% count(Gender)
pm_modified %>% 
  group_by(Gender) %>% 
  summarise(mean = mean(Money_spent))
```

### Observations

-   Outliers in both groups
-   Based on median, females spend more money than males.
-   In the density plot we can see that the distributions overlap to quite an extent, females spend more and there is more variability in male spending.

------------------------------------------------------------------------

<button>[Checking Assumptions]{.button_top}</button>

------------------------------------------------------------------------

## Hypotheses:

-   H0​: μ male spending​=μ female spending

-   Ha​: μ male spending ≠ μ female spending

## - Check for Normality

```{r}
pm_modified %>%
  gf_density( ~ Money_spent,
              fill = ~ Gender,
              alpha = 0.5,
              title = "Money_spent by males and females") %>%
  gf_facet_grid(~ Gender) %>% 
  gf_fitdistr(dist = "dnorm")
```

-   both are right skewed and have sharp peaks...

```{r}
shapiro.test(pm_modified$Money_spent[pm_modified$Gender== "Female"])
```

p value-\> 0.0000000000008961

```{r}
shapiro.test(pm_modified$Money_spent[pm_modified$Gender== "Male"])
```

p value-\> 0.00000000001136

#### *we can reject the null hypothesis and go forward with our alternative hypothesis based on w values, we can say data is not normally distributed*

## - Check for Variances

```{r}
var.test(Money_spent ~ Gender, data = pm_modified, 
         conf.int = TRUE, conf.level = 0.95) %>% 
  broom::tidy()
```

#### *p value= 0.17 hence variances can be considered approximately equal. we do not reject the null hypothesis.*

### -

### Difference in Means:

```{r}
obs_diff_pm <- diffmean(Money_spent ~ Gender, data = pm_modified) 
obs_diff_pm
```

------------------------------------------------------------------------

## <button>[Inferences]{.button_top}</button>

------------------------------------------------------------------------

# <u>-Using Parametric t.test</u>

```{r}
mosaic::t_test(Money_spent ~Gender, data = pm_modified) %>% 
  broom::tidy()
```

### with a high p value of 0.8, we can say that means of male and female pocket money spendings are not significantly different from one another.

# <u>-Using Mann-Whitney </u>

--data variables not distributed normally

```{r}
wilcox.test(Money_spent ~ Gender, data = pm_modified, 
            conf.int = TRUE, 
            conf.level = 0.95) %>% 
  broom::tidy()
```

### p value of 0.3, we fail to reject our null hypothesis. 

# <u>-Permutation </u>

```{r}
null_dist_pm <- 
  do(4999) * diffmean(data =pm_modified, Money_spent ~ shuffle(Gender))
head(null_dist_pm, n = 15)
```

```{r}
gf_histogram(data = null_dist_pm, ~ diffmean, bins = 25) %>%
  gf_vline(xintercept = obs_diff_pm, 
           colour = "blue", linewidth = 2,
           title = "Null Distribution by Permutation", 
           subtitle = "Histogram") %>% 
  gf_labs(x = "Difference in Means")
###
gf_ecdf(data = null_dist_pm, ~ diffmean, 
        linewidth = 2) %>%
  gf_vline(xintercept = obs_diff_pm, 
           colour = "blue", linewidth = 1,
           title = "Null Distribution by Permutation", 
           subtitle = "Cumulative Density") %>% 
  gf_labs(x = "Difference in Means")
```

```{r}
1-prop1(~ diffmean <= obs_diff_pm, data = null_dist_pm)
```

### no strong difference between the groups being compared, female and male pocket money spemdings are approx same. 
