---
title: "A1: Counts"
---

## Code Replication

```{r setup, echo=FALSE}
suppressMessages({
 library(tidyverse)
library(mosaic)
library(ggformula)
library(skimr)
library(readr)
library(jsonlite)
})
```

```         
```

```{r}
taxi <- read_csv("https://vincentarelbundock.github.io/Rdatasets/csv/modeldata/taxi.csv")
taxi
```

```{r}
glimpse(taxi)
```

```{r}
inspect(taxi)
```

```{r}
skim(taxi)
```

```{r}
## Convert `dow`, `local`, and `month` into ordered factors
taxi_modified <- taxi %>%
  mutate(
    dow = factor(dow,
      levels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"),
      labels = c("Mon", "Tue", "Wed", "Thu", "Fri", "Sat", "Sun"),
      ordered = TRUE
    ),
    ##
    local = factor(local,
      levels = c("no", "yes"),
      labels = c("no", "yes"),
      ordered = TRUE
    ),
    ##
    month = factor(month,
      levels = c("Jan", "Feb", "Mar", "Apr"),
      labels = c("Jan", "Feb", "Mar", "Apr"),
      ordered = TRUE
    )
  )
taxi_modified %>% glimpse()
```

```{r}
gf_bar(~tip, data = taxi_modified) %>%
  gf_labs(title = "Plot 1A: Counts of Tipss")
```

```{r}
taxi_modified %>%
  gf_bar(~tip,
    fill = ~local, 
    position = "dodge"
  ) %>%
  gf_labs(title = "Plot 2A: Dodged Bar Chart")
```

```{r}
taxi_modified %>%
  gf_bar(~company,
    fill = ~tip,
    position = "fill"
  ) %>%
  gf_labs(title = "Plot 2A: Dodged Bar Chart") %>%
  gf_theme(theme(axis.text.x = element_text(size = 6, angle = 45, hjust = 1)))
```

```{r}
gf_bar(~dow, fill = ~tip, position="fill", data = taxi_modified) %>%
  gf_labs(title = "Plot C: Counts of Tips by Day of Week")
```

```{r}
gf_bar(~month, fill = ~tip,  data = taxi_modified) %>%
  gf_labs(title = "Plot D: Counts of Tips by Month")
```

# Pokémon

```{r}
pokemon <- fromJSON("https://calmcode.io/static/data/pokemon.json")


pretty_json <- toJSON(pokemon, pretty = TRUE, auto_unbox = TRUE)


write(pretty_json, file = "pretty_pokemon.json")


```

## Examining

```{r}
glimpse(pokemon)
```

```{r}
skim(pokemon)
```

```{r}
inspect(pokemon)
```

## Data munging & Data Dictionary

-   tried converting list into factor, could not.

-   leaving type as it is.

```{r, echo=FALSE}
data_dictionary <- data.frame(
  Variable_Name = c("Name", "Type", "HP", "Attack", "Total"),
  Data_Type = c("character", "factor", "integer", "integer", "integer"),
  Description = c(
    "The name of the Pokémon.",
    "The type(s) of the Pokémon, affecting battle strengths and weaknesses.",
    "Total health of the Pokémon in battles (Hit Points).",
    "Damage dealt by the Pokémon's attacks.",
    "Total HP overall."
  ),
  stringsAsFactors = FALSE  # Prevent automatic conversion to factors
)


print(data_dictionary)


```

## Questions

```{r}
pokemon_summary <- pokemon %>%
group_by(type) %>%
summarize(avg_hp = mean(hp), avg_attack = mean(attack))

pokemon_summary
  
```

average hp and attack for each type

### Abandoning this data set as list needs to be converted into factor to get accurate data viz.

# Fertility DataSet

```{r}
fertility<- read_delim("../../data/Fertility.csv")
print(head(fertility))
```

## Examining

```{r}
glimpse(fertility)
```

```{r}
skim(fertility)
```

```{r}
inspect(fertility)
```

## Data Munging and Dictionary

```{r, echo=FALSE}
data_dictionary <- data.frame(
  Variable_Name = c("morekids", "gender1", "gender2", "hispanic", "age"),
  Data_Type = c("factor", "factor", "factor", "factor", "integer"),
  Description = c(
    "do the respondents have more than 2 kids",
    "gender of the first child",
    "gender of the second child",
    "are they hispanic",
    "age"
  ),
  stringsAsFactors = FALSE  # Prevent automatic conversion to factors
)


print(data_dictionary)
```

```{r}
fertility_modified <- fertility %>%
mutate(
    morekids= as.factor(morekids),  
    gender1 = as.factor(gender1),
    gender2 = as.factor(gender2),
    hispanic = as.factor(hispanic),
    other = as.factor(other),
    
  )
glimpse(fertility_modified)
```

## Bar graphs

```{r}
gf_bar(~morekids, data = fertility_modified) %>%
  gf_labs(title = "")

```

-   Does the Hispanic ethnic group tend to have a higher number of children?

    ```{r}
    fertility_modified %>%
      gf_bar(~morekids, 
             fill = ~hispanic, 
             position = "dodge") %>%
      
      gf_labs(title = "Plot: Dodged Bar Chart")
    ```

> #### Inferences
>
> -   majority, regardless of their ethnicity, indicate they do not have more kids.
>
> -   vast majority of hispanic respondents seem to not have more kids.

```{r}
fertility_modified %>%
  gf_bar(~morekids, 
         fill = ~gender1, 
         position = "dodge") %>%
  
  gf_labs(title = "Plot: Dodged Bar Chart")
```

> #### Inference
>
> -   people with male kids as their firstborn prefer to not have more kids.
