---
title: "A2-Dataset-3"
format:
  html:
    css: styles.css
---

# Movie Profits

```{r setup, echo=FALSE}
suppressMessages({
library(tidyverse)
library(mosaic)
library(skimr)
library(ggformula)
library(knitr)
})
```

------------------------------------------------------------------------

<button>[Reading & Examining the Data]{.button_top}</button>

------------------------------------------------------------------------

```{r}
movieprofit <- read_delim("../../data/movie_profit.csv")
print(head(movieprofit))

```

```{r}
glimpse(movieprofit)
```

```{r}
inspect(movieprofit)
```

```{r}
skim(movieprofit)
```

------------------------------------------------------------------------

<button>[Data Munging and Data Dictionary]{.button_top}</button>

------------------------------------------------------------------------

```{r}
movieprofit_modified<- movieprofit %>%
  mutate(
    mpaa_rating = as.factor(mpaa_rating),
    genre = as.factor(genre),
    decade = as.factor(decade)
  )
glimpse(movieprofit_modified)
```

```{r}
data_dictionary <- data.frame(
  Variable = c("release_date", "movie", "production_budget", "domestic_gross",
               "worldwide_gross", "distributor", "mpaa_rating", "genre", 
               "profit_ratio", "decade"),
  Data_Type = c("Date", "Character", "Numeric", "Numeric",
                "Numeric", "Character", "Factor", "Factor", 
                "Numeric", "Factor"),
  Description = c("The release date of the movie", "Title of the movie", 
                  "Budget allocated for the movie", "Gross revenue earned domestically", 
                  "Total gross revenue worldwide", "Company distributing the movie", 
                  "Rating assigned by the MPAA", "Genre of the movie", 
                  "Ratio of profit to production budget", "decade in which the movie was released")
)


kable(data_dictionary)
```

-   **Qualitative Variables**: movie, distributor, mpaa_rating, genre, decade

-   **Quantitative Variables**: production_budget, domestic_gross, worldwide_gross, profit_ratio

-   **Temporal Variable**: release_date

------------------------------------------------------------------------

<button>[Plotting graphs]{.button_top}</button>

------------------------------------------------------------------------

```{r}

gf_bar(genre ~ profit_ratio | distributor, data = movieprofit_modified) 

```

```{r}
glimpse(movieprofit_modified)
```

```{r}
median_profit_data <- movieprofit_modified %>%
  group_by(genre, distributor) %>%
  summarize(median_profit_ratio = median(profit_ratio), .groups = "drop")  


ggplot(median_profit_data, aes(x = median_profit_ratio, y = genre)) +
  geom_col() +  
  facet_wrap(~ distributor) + 
  labs(
    title = "ratio of profits to genre",
    x = "Median Profit Ratio",
    y = "Genre"
  ) 


```

-   horizontal bar plots

-   genre and median of profit ratio are the two variables being plotted

-   action and horror

-   facet_wrap(\~ distributor) to get separate plots for each distributor

-   would have hate to mutate and calculate profit ratio
