---
title: "index"
---

```{r}
library(tidyverse)
library(mosaic)
library(ggformula)
library(infer)
library(broom) # Clean test results in tibble form
library(resampledata) # Datasets from Chihara and Hesterberg's book
library(openintro) # More datasets
```

```{r}
set.seed(40)  # for replication
# Data as individual vectors ( for t.tests etc)
y <- rnorm(50, mean = 2, sd = 2)

# And as tibble too
mydata <- tibble(y = y)
mydata
```

##tibble- dataframe

##y \<- rnorm- generate 50 random numbers

##so we have vector(array?) y with 50 normally distributed random numbers - data is symetrically distribted around the mean

```{r}
mydata %>%
    gf_density(~y) %>% ##distribution of y values 
    gf_fitdistr(dist = "dnorm") %>% ##normal distribution based on mean and sd? always a symmetrical bell curve 
    gf_labs(title = "Densities of Original Data Variables", subtitle = "Compared with Normal Density")

```

```{r}
# t-test
t1 <- mosaic::t_test(
          y, # Name of variable
          mu = 0, # belief of population mean
          alternative = "two.sided") %>% # Check both sides
  
  broom::tidy() # Make results presentable, and plottable!!
t1
```

```{r}
mean_belief_pop <- 0  # Assert our belief
# Sample Mean
mean_y <- mean(y)
mean_y
```

```{r}
## Sample standard error
std_error <- sd(y)/sqrt(length(y))
std_error
```

```{r}
## Confidence Interval of Observed Mean
conf_int <- tibble(ci_low = mean_y - 1.96 * std_error, ci_high = mean_y + 1.96 *
    std_error)
conf_int
```

```{r}
## Difference between actual and believed mean
mean_diff <- mean_y - mean_belief_pop
mean_diff
```

```{r}
## Test Statistic
t <- mean_diff/std_error
t
```

##sample mean is 2.04, likelihood of zero being the mean is very low

#p value, t-test

##based on the assumption that our sample is a bell curve

##permutation\]

### Paired t.test

```{r}
library(tidyverse)
library(mosaic)
library(broom) # Tidy Test data
library(resampledata3) # Datasets from Chihara and Hesterberg's book
library(gt) # for tabl
```

----paired data- quantitative measuremens for same set of people

```{r}
data("Diving2017", package = "resampledata3")
Diving2017
Diving2017_inspect <- inspect(Diving2017)
Diving2017_inspect$categorical
Diving2017_inspect$quantitative
```

--- 2 quants and 2 qual variables

-   data is made up of paired observations

wide- long form data

easier to plot with long form data

```{r}
Diving2017_long <- Diving2017 %>%
  pivot_longer(
    cols = c(Final, Semifinal),
    names_to = "race",
    values_to = "scores"
  )
Diving2017_long
```

```{r}
Diving2017_long %>%
  gf_density(~scores,
    fill = ~race,
    alpha = 0.5,
    title = "Diving Scores"
  ) %>%
  gf_facet_grid(~race) %>%
  gf_fitdistr(dist = "dnorm")

```

--- samples are not gaussian

`{r} ---} Diving2017_long %>%   gf_col(     fct_reorder(Name, scores) ~ scores,     fill = ~race,     alpha = 0.5,     position = "dodge",     xlab = "Scores",     ylab = "Name",     title = "Diving Scores"   )`

```{r}
Diving2017_long %>%
  gf_boxplot(
    scores ~ race,
    fill = ~race,
    alpha = 0.5,
    xlab = "Race",
    ylab = "Scores",
    title = "Diving Scores"
  )
```

```{r}
shapiro.test(Diving2017$Final)
shapiro.test(Diving2017$Semifinal)
```

---if p value is v small then it means that the final scores are not normally distributed

## Hypothesis ß
